\documentclass{sig-alternate-ipsn09}

\usepackage{graphicx}
\usepackage{times}
\usepackage{epsfig}
\usepackage{psfrag}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{mathenv}
\usepackage{epstopdf}
%\usepackage{algorithmic}
%\usepackage{algorithm}

\usepackage{fancyhdr}


\begin{document}

\title{A Sample {\ttlit ACM} SIG Proceedings Paper in LaTeX
Format\titlenote{(Does NOT produce the permission block, copyright information nor page numbering). Supported by ACM.}}
%
% You need the command \numberofauthors to handle the 'placement
% and alignment' of the authors beneath the title.
%
% For aesthetic reasons, we recommend 'three authors at a time'
% i.e. three 'name/affiliation blocks' be placed beneath the title.
%
% NOTE: You are NOT restricted in how many 'rows' of
% "name/affiliations" may appear. We just ask that you restrict
% the number of 'columns' to three.
%
% Because of the available 'opening page real-estate'
% we ask you to refrain from putting more than six authors
% (two rows with three columns) beneath the article title.
% More than six makes the first-page appear very cluttered indeed.
%
% Use the \alignauthor commands to handle the names
% and affiliations for an 'aesthetic maximum' of six authors.
% Add names, affiliations, addresses for
% the seventh etc. author(s) as the argument for the
% \additionalauthors command.
% These 'additional authors' will be output/set for you
% without further effort on your part as the last section in
% the body of your article BEFORE References or any Appendices.

\numberofauthors{8} %  in this sample file, there are a *total*
% of EIGHT authors. SIX appear on the 'first-page' (for formatting
% reasons) and the remaining two appear in the \additionalauthors section.
%
\author{
% You can go ahead and credit any number of authors here,
% e.g. one 'row of three' or two rows (consisting of one row of three
% and a second row of one, two or three).
%
% The command \alignauthor (no curly braces needed) should
% precede each author name, affiliation/snail-mail address and
% e-mail address. Additionally, tag each line of
% affiliation/address with \affaddr, and tag the
% e-mail address with \email.
%
% 1st. author
\alignauthor
Ben Trovato\titlenote{Dr.~Trovato insisted his name be first.}\\
       \affaddr{Institute for Clarity in Documentation}\\
       \affaddr{1932 Wallamaloo Lane}\\
       \affaddr{Wallamaloo, New Zealand}\\
       \email{trovato@corporation.com}
% 2nd. author
\alignauthor
G.K.M. Tobin\titlenote{The secretary disavows
any knowledge of this author's actions.}\\
       \affaddr{Institute for Clarity in Documentation}\\
       \affaddr{P.O. Box 1212}\\
       \affaddr{Dublin, Ohio 43017-6221}\\
       \email{webmaster@marysville-ohio.com}
% 3rd. author
\alignauthor Lars Th{\o}rv{\"a}ld\titlenote{This author is the
one who did all the really hard work.}\\
       \affaddr{The Th{\o}rv{\"a}ld Group}\\
       \affaddr{1 Th{\o}rv{\"a}ld Circle}\\
       \affaddr{Hekla, Iceland}\\
       \email{larst@affiliation.org}
\and  % use '\and' if you need 'another row' of author names
% 4th. author
\alignauthor Lawrence P. Leipuner\\
       \affaddr{Brookhaven Laboratories}\\
       \affaddr{Brookhaven National Lab}\\
       \affaddr{P.O. Box 5000}\\
       \email{lleipuner@researchlabs.org}
% 5th. author
\alignauthor Sean Fogarty\\
       \affaddr{NASA Ames Research Center}\\
       \affaddr{Moffett Field}\\
       \affaddr{California 94035}\\
       \email{fogartys@amesres.org}
% 6th. author
\alignauthor Charles Palmer\\
       \affaddr{Palmer Research Laboratories}\\
       \affaddr{8600 Datapoint Drive}\\
       \affaddr{San Antonio, Texas 78229}\\
       \email{cpalmer@prl.com}
}
% There's nothing stopping you putting the seventh, eighth, etc.
% author on the opening page (as the 'third row') but we ask,
% for aesthetic reasons that you place these 'additional authors'
% in the \additional authors block, viz.
\additionalauthors{Additional authors: John Smith (The Th{\o}rv{\"a}ld Group,
email: {\texttt{jsmith@affiliation.org}}) and Julius P.~Kumquat
(The Kumquat Consortium, email: {\texttt{jpkumquat@consortium.net}}).}
\date{30 July 1999}
% Just remember to make sure that the TOTAL number of authors
% is the number that will appear on the first page PLUS the
% number that will appear in the \additionalauthors section.

%Sections go here.  An example of figures is shown in Figure~\ref{fig:example}.
%\begin{figure}
%\centering
%\epsfig{file=fly.eps}
%\caption{A sample black and white graphic (.eps format).}
%\label{fig:example}
%\end{figure}


\maketitle
\begin{abstract}
\input{abstract}
\end{abstract}

\input{introduction}

\input{background}

%\input{assumptions}

%\input{physicalsystem}

%\input{networksystem}

\section{Methodology}
Methodology goes here


\section{Conclusions}
Conclusion goes here.

%ACKNOWLEDGMENTS are optional
\section*{Acknowledgments}
Acknowledgement goes here.

%
% The following two commands are all you need in the
% initial runs of your .tex file to
% produce the bibliography for the citations in your paper.
\bibliographystyle{abbrv}
\bibliography{sigproc}  % sigproc.bib is the name of the Bibliography in this case
% You must have a proper ".bib" file
%  and remember to run:
% latex bibtex latex latex
% to resolve all references

\begin{thebibliography}{10}

\setlength{\itemsep}{-0.01mm}
\footnotesize

\bibitem{cyphy}
{IEEE} workshop on design, modeling and evaluation of cyber physical systems.

\bibitem{omnet}
The {OMNeT}++ discrete event simulation system.

\bibitem{aikat2003variability}
J.~Aikat, J.~Kaur, F.~Smith, and K.~Jeffay.
\newblock Variability in tcp round-trip times.
\newblock In {\em Internet Measurement Conference: Proceedings of the 3 rd ACM
  SIGCOMM conference on Internet measurement}, volume~27, pages 279--284, 2003.

\bibitem{5622003}
R.~Akella, F.~Meng, D.~Ditch, B.~McMillin, and M.~Crow.
\newblock Distributed power balancing for the freedm system.
\newblock In {\em Smart Grid Communications (SmartGridComm), 2010 First IEEE
  International Conference on}, pages 7 --12, October 2010.

\bibitem{alur94}
R.~Alur and D.~L. Dill.
\newblock A theory of timed automata.
\newblock {\em Theoretical Computer Science}, 126(2):183--235, 1994.

\bibitem{Bak2010}
S.~Bak, A.~Greer, and S.~Mitra.
\newblock Hybrid cyberphysical system verification with simplex using discrete
  abstractions.
\newblock In {\em Real-Time and Embedded Technology and Applications Symposium
  (RTAS), 2010 16th IEEE}, pages 143 --152, april 2010.

\bibitem{5587717}
S.~Bensalem, A.~Legay, T.-H. Nguyen, J.~Sifakis, and R.~Yan.
\newblock Incremental invariant generation for compositional design.
\newblock In {\em Theoretical Aspects of Software Engineering (TASE), 2010 4th
  IEEE International Symposium on}, pages 157 --167, aug. 2010.

\bibitem{GarlanKrogh2010}
A.~Bhave, B.~Krogh, D.~Garlan, and B.~Schmerl.
\newblock Multi-domain modeling of cyber-physical systems using architectural
  views.
\newblock In {\em Proceedings of the 1st Analytic Virtual Integration of
  Cyber-Physical Systems Workshop.}, 30 November 2010.
\newblock Co-located with RTSS 2010.

\bibitem{branicky98}
M.~S. Branicky.
\newblock Multiple lyapunov functions and other analysis tools for switched and
  hybrid systems.
\newblock {\em IEEE Transactions on Automatic Control}, 43(4):475--482, 1998.

\bibitem{Buttazzo_IEEE_Jornl_2002}
G.~Buttazzo, G.~Lipari, M.~Caccamo, and L.~Abeni.
\newblock Elastic scheduling for flexible workload management.
\newblock {\em Computers, IEEE Transactions on}, 51(3):289 --302, mar 2002.

\bibitem{chutinan03}
A.~Chutinan and B.~H. Krogh.
\newblock Computational techniques for hybrid system verification.
\newblock {\em IEEE Transactions on Automatic Control}, 48:64--75, January
  2003.

\bibitem{Alfaro}
L.~de~Alfaro and M.~Stoelinga.
\newblock Interfaces: A game-theoretic framework to reason about open systems.
\newblock In {\em FOCLASA 03: Proceedings of the 2nd International Workshop on
  Foundations of Coordination Languages and Software Architectures, Electronic
  Notes on Theoretical Computer Science}. Elsevier Science Publishers, 2003.

\bibitem{DerlerLeeSangiovanniVincentelli12_ModelingCyberPhysicalSystems}
P.~Derler, E.~A. Lee, and A.~Sangiovanni-Vincentelli.
\newblock Modeling cyber-physical systems.
\newblock {\em Proceedings of the IEEE (special issue on CPS)}, 100(1):13 --
  28, January 2012.

\bibitem{AdaptiveScheduling_DASC_1999}
B.~Doerr, T.~Venturella, R.~Jha, C.~Gill, and D.~Schmidt.
\newblock Adaptive scheduling for real-time, embedded information systems.
\newblock In {\em Digital Avionics Systems Conference, 1999. Proceedings.
  18th}, volume 1/17 pp. vol.1, pages 2.D.5--1 --2.D.5--9 vol.1, nov 1999.

\bibitem{donkers11}
M.~C.~F. Donkers, W.~P. M.~H. Heemels, N.~van~de Wouw, and L.~Hetel.
\newblock Stability analysis of networked control systems using a switched
  linear systems approach.
\newblock {\em IEEE Transactions on Automatic Control}, 56:2101--2115, 2011.

\bibitem{floyd1994tcp}
S.~Floyd.
\newblock Tcp and explicit congestion notification.
\newblock {\em ACM SIGCOMM Computer Communication Review}, 24(5):8--23, 1994.

\bibitem{guo2003bayesian}
D.~Guo and X.~Wang.
\newblock Bayesian inference of network loss and delay characteristics with
  applications to tcp performance prediction.
\newblock {\em Signal Processing, IEEE Transactions on}, 51(8):2205--2218,
  2003.

\bibitem{henia_ernst_rtss_2007}
R.~Henia and R.~Ernst.
\newblock Scenario aware analysis for complex event models and distributed
  systems.
\newblock In {\em IEEE Real-Time Systems Symposium}, pages 171--180, Los
  Alamitos, CA, USA, 2007.

\bibitem{henzinger96}
T.~A. Henzinger.
\newblock The theory of hybrid automata.
\newblock In {\em IEEE Symposium on Logic in Computer Science}, pages 278--292,
  1996.

\bibitem{hespanha07}
J.~P. Hespanha, P.~Naghshtabrizi, and Y.~Xu.
\newblock A survey of recent results in networked control systems.
\newblock {\em Proceedings of the IEEE}, 95:138--162, 2007.

\bibitem{Hoare85}
C.~Hoare.
\newblock {\em Communicating Sequential Processes}.
\newblock Prentice Hall, 1985.

\bibitem{hollot2001control}
C.~Hollot, V.~Misra, D.~Towsley, and W.~Gong.
\newblock A control theoretic analysis of red.
\newblock In {\em INFOCOM 2001. Twentieth Annual Joint Conference of the IEEE
  Computer and Communications Societies. Proceedings. IEEE}, volume~3, pages
  1510--1519. IEEE, 2001.

\bibitem{huang11}
A.~Q. Huang, M.~L. Crow, G.~T. Heydt, J.~P. Zheng, and S.~J. Dale.
\newblock {The Future Renewable Electric Energy Delivery and Management
  (FREEDM) System: The energy internet}.
\newblock {\em Proceedings of the IEEE}, 99(1):133--148, Jan. 2011.

\bibitem{jiang2002passive}
H.~Jiang and C.~Dovrolis.
\newblock Passive estimation of tcp round-trip times.
\newblock {\em ACM SIGCOMM Computer Communication Review}, 32(3):75--88, 2002.

\bibitem{SmartGridLoadScheduling}
I.~Koutsopoulos and L.~Tassiulas.
\newblock Control and optimization meet the smart power grid: scheduling of
  power demands for optimal energy management.
\newblock In {\em Proceedings of the 2nd International Conference on
  Energy-Efficient Computing and Networking}, e-Energy '11, pages 41--50, 2011.

\bibitem{DAC_2012_CPS_verification}
P.~Kumar, D.~Goswami, S.~Chakraborty, A.~Annaswamy, K.~Lampka, and L.~Thiele.
\newblock A hybrid approach to cyber-physical systems verification.
\newblock In {\em 49th ACM/EDAC/IEEE Design Automation Conference (DAC)}, pages
  688 --696, june 2012.

\newpage

\bibitem{ReconfigurationCBSECRTST2012}
P.~Kumar, N.~Stoimenov, and L.~Thiele.
\newblock An algorithm for online reconfiguration of resource reservations for
  hard real-time systems.
\newblock In {\em ECRTS}, pages 245--254, 2012.

\bibitem{liberzon03}
D.~Liberzon.
\newblock {\em Switching in Systems and Control}.
\newblock Birkhauser, Boston, 2003.

\bibitem{liu00}
J.~Liu.
\newblock {\em Real-Time Systems}.
\newblock Prentice Hall, 2000.

\bibitem{martin2000analysis}
H.~Martin, A.~McGregor, and J.~Cleary.
\newblock Analysis of internet delay times.
\newblock {\em Measurement}, 2000.

\bibitem{OwickiGries1976}
S.~Owicki and D.~Gries.
\newblock An axiomatic proof technique for parallel programs.
\newblock {\em Acta Informatica}, 6:319--340, 1976.

\bibitem{paul12thesis}
T.~Paul.
\newblock {\em Unified Knowledge Model for Stability Analysis in Cyber Physical
  Systems}.
\newblock Missouri University of Science and Technology, 2012.

\bibitem{paul2011}
T.~Paul, J.~Kimball, M.~Zawodniok, T.~Roth, and B.~McMillin.
\newblock Invariants as a unified knowledge model for cyber-physical systems.
\newblock In {\em Service-Oriented Computing and Applications (SOCA), 2011 IEEE
  International Conference on}, pages 1 --8, dec. 2011.



\bibitem{pei2009passive}
Y.~Pei, H.~Wang, and S.~Cheng.
\newblock A passive method to estimate tcp round trip time from nonsender-side.
\newblock In {\em Computer Science and Information Technology, 2009. ICCSIT
  2009. 2nd IEEE International Conference on}, pages 43--47. IEEE, 2009.



\bibitem{quet2002guidelines}
P.~Quet, S.~Chellappan, A.~Durresi, M.~Sridharan, H.~{\"O}zbay, and R.~Jain.
\newblock Guidelines for optimizing multi-level ecn, using fluid flow based tcp
  model.
\newblock {\em Proc. ITCOM-2002}, pages 106--116, 2002.

%\newpage

\bibitem{ramakrishnan1999proposal}
K.~Ramakrishnan and S.~Floyd.
\newblock A proposal to add explicit congestion notification (ecn) to ip.
\newblock Technical report, RFC 2481, January, 1999.

\bibitem{ramakrishnan2001addition}
K.~Ramakrishnan, S.~Floyd, D.~Black, et~al.
\newblock The addition of explicit congestion notification (ecn) to ip, 2001.

\bibitem{real_crespo_rts_2004}
J.~Real and A.~Crespo.
\newblock Mode change protocols for real-time systems: A survey and a new
  proposal.
\newblock {\em Real-Time Systems}, 26(2):161--197, 2004.

\bibitem{sha_rts_1989}
L.~Sha, R.~Rajkumar, J.~Lehoczky, , and K.~Ramamritham.
\newblock Mode change protocols for priority-driven preemptive scheduling.
\newblock {\em Real-Time Systems}, 1(3):243--264, 1989.

\bibitem{shakkottai2004rtt}
S.~Shakkottai, R.~Srikant, N.~Brownlee, A.~Broido, et~al.
\newblock The rtt distribution of tcp flows in the internet and its impact on
  tcp-based flow control.
\newblock 2004.

\bibitem{DBLP:SitzoffG93}
M.~Sintzoff and F.~Geurts.
\newblock Analysis of dynamical systems using predicate transformers -
  attraction and composition.
\newblock In {\em Analysis of Dynamical and Cognitive Systems}, pages 227--260,
  1993.

\bibitem{stoimenov_date_2009}
N.~Stoimenov, S.~Perathoner, and L.~Thiele.
\newblock Reliable mode changes in real-time systems with fixed priority or edf
  scheduling.
\newblock In {\em Design, Automation and Test in Europe}, pages 99--104. IEEE,
  April 2009.

\bibitem{tomlin03}
C.~J. Tomlin, I.~Mitchell, A.~M. Bayen, and M.~Oishi.
\newblock Computational techniques for the verification of hybrid systems.
\newblock {\em Proceedings of the IEEE}, 91:986--1001, July 2003.

\bibitem{omnetpaper}
A.~Varga.
\newblock The omnet++ discrete event simulation system.
\newblock {\em Proceedings of the European Simulation Multiconference
  (ESM'2001)}, June 2001.

\bibitem{FeedbackScheduling07}
F.~Xia, G.~Tian, and Y.~Sun.
\newblock Feedback scheduling: an event-driven paradigm.
\newblock {\em SIGPLAN Not.}, 42(12):7--14, Dec. 2007.

\bibitem{ye98impulse}
H.~Ye, A.~N. Michel, and L.~Hou.
\newblock Stability analysis of systems with impulse effects.
\newblock {\em IEEE Transactions on Automatic Control}, 43(12):1719--1723,
  1998.

\bibitem{ye98hybrid}
H.~Ye, A.~N. Michel, and L.~Hou.
\newblock Stability theory for hybrid dynamical systems.
\newblock {\em IEEE Transactions on Automatic Control}, 43(4):461--474, 1998.

\bibitem{Zhu:2010:MEE:1795194.1795196}
Y.~Zhu, E.~Westbrook, J.~Inoue, A.~Chapoutot, C.~Salama, M.~Peralta, T.~Martin,
  W.~Taha, M.~O'Malley, R.~Cartwright, A.~Ames, and R.~Bhattacharya.
\newblock Mathematical equations as executable models of mechanical systems.
\newblock In {\em Proceedings of the 1st ACM/IEEE International Conference on
  Cyber-Physical Systems}, ICCPS '10, pages 1--11, New York, NY, USA, 2010.
  ACM.

\end{thebibliography}


%
% ACM needs 'a single self-contained file'!
%
%APPENDICES are optional
%\balancecolumns
\appendix
%Appendix A

Appendix goes here.

% That's all folks!
\end{document}
